---
title: "TABLE EXPLORATORY DATA ANALYSIS REPORT"
output:
  html_document: 
    theme: journal
    toc: yes
    toc_depth: 6
    df_print: paged
    fig_width: 12
    fig_height: 7
params:
  data: data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r global_options, include = FALSE}
library(rmarkdown)
library(dplyr)

num_discrete <- SplitColType(params$data)$num_discrete
num_continuous <- SplitColType(params$data)$num_continuous
num_all_missing <- SplitColType(params$data)$num_all_missing

```

### Descriptive statistics summary
The data is **`r format(object.size(data), units = "auto")`** in size. There are  **`r format(nrow(data), big.mark = ",")`** rows and **`r format(ncol(data), big.mark = ",")`** columns (feartrues). Of all **`r format(ncol(data), big.mark = ",")`** columns, **`r I(num_discrete)`** are discrete, **`r I(num_continuous)`** are continuous, and **`r I(num_all_missing)`** are all missing. There are **`r format(sum(is.na(data)), big.mark = ",")`** missing values out of  **`r format(nrow(data)*ncol(data), big.mark = ",")`** total data points

#### Data Structure (Text)

```{r data_structure, echo=FALSE}
as.data.frame(str(data))
```

### 缺失值检测
下图为表中缺失值在各个字段中的分布状况。
```{r plot_missing, echo=FALSE}
PlotMissing(data)
```


### Duplicated Observation
The following table shows the number of duplicated observation in each columns. Sometimes, analysts would like to make sure data in some specific columns is unique. This table will help to check duplicated observation in each volumns.
``` {r DetectDup, echo=FALSE}
DetectDup(data)
```

### Continuos Correlation Coefficients
Below shows the correlation coefficient between continuous variables. Due to the number of variables, there only display top 10 variables, which have higher mean of correlation coefficient with all other variables. Those 10 variables have higher importance than other variables that shows lower correlation with all other variables.

```{r ContinuousCorrelation, echo=FALSE}
ContinuousCorrelation(data)
```

### Discrete correlation coefficients

Below is the correlation coefficients between each discrete correlation.

```{r echo=FALSE, warning=FALSE}
DiscreteCorrelation(data)
```


