---
title: "KG EDA REPORT TABLE STATISTICS"
author: 'Hengchang Knowledge Graph'
output:
  html_document: 
    theme: journal
    toc: yes
    toc_depth: 6
    df_print: paged
    fig_width: 12
    fig_height: 7
params:
  data: data
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r global_options, include = FALSE}
library(rmarkdown)
library(dplyr)

data <- params$data
num_discrete <- SplitColType(params$data)$num_discrete
num_continuous <- SplitColType(params$data)$num_continuous
num_all_missing <- SplitColType(params$data)$num_all_missing

```

### 数据基础统计值
数据大小为**`r format(object.size(data), units = "auto")`**. 表中有 **`r format(nrow(data), big.mark = ",")`** 行和 **`r format(ncol(data), big.mark = ",")`** 列（字段）. 在所有 **`r format(ncol(data), big.mark = ",")`**列中, **`r I(num_discrete)`** 个是离散型变量, **`r I(num_continuous)`** 个是连续型变量, 同时 **`r I(num_all_missing)`** 个全部缺失变量. 共有 **`r format(sum(is.na(data)), big.mark = ",")`** 缺失的观测值在 **`r format(nrow(data)*ncol(data), big.mark = ",")`** 个总观测值中.

#### Data Structure (Text)

```{r data_structure, echo=FALSE}
as.data.frame(str(data))
```

### 缺失值检测
下图为表中缺失值在各个字段中的分布状况。
```{r plot_missing, echo=FALSE}
PlotMissing(data)
```


### Duplicated Observation
The following table shows the number of duplicated observation in each columns. Sometimes, analysts would like to make sure data in some specific columns is unique. This table will help to check duplicated observation in each volumns.
``` {r DetectDup, echo=FALSE}
DetectDup(data)
```

### Continuos Correlation Coefficients
Below shows the correlation coefficient between continuous variables. Due to the number of variables, there only display top 10 variables, which have higher mean of correlation coefficient with all other variables. Those 10 variables have higher importance than other variables that shows lower correlation with all other variables.

```{r ContinuousCorrelation, echo=FALSE}
ContinuousCorrelation(data)
```

### 离散变量的相关关系矩阵

该离散变量相关关系矩阵, 没有计算缺失值在70%以上的字段, 因为大量缺失的字段计算的相关关系并不显著, 没有实际意义. 其次, 剔除了观测值完全唯一的字段, 这些字段会导致计算相关关系时, 平均方差为0. 对所有计算过的相关关系中, 保留字段与其他字段相关关系最大值排序的前20列字段. 展示该20列数据的相关关系.

该类别型变量相关关系计算中, 将各个类别用数字进行了编译, 然后对数据进行了pearson correlation计算, 返回的相关关系系数可能存在偏差. 

```{r echo=FALSE, warning=FALSE}
DiscreteCorrelation(data)
```


